week getbackontrack

### 2024-11-12 descriptivestry.Rmd
prettyplotsindescriptives

```{r df_ego data}
df_ego <- fload("./data/processed/df_ego_20241108.rda")
```

@@

    -   descriptives (mean etc.)

```{r sum gender}
summary(df_ego$gender)

    -   overall

```{r hist gender}
# Histogram of prestige scores for Wave 1  
hist(df_ego$gender, breaks = , main = "Distribution of gender",     xlab = "Gender", ylab = "Frequency", col = "#B3DE69") # INSERT YEARS OF WAVE/TIME FRAME STILL
```

```         
-   Gender per department
```

```{r gender per dep.}
# STILL DO 
```

@@

```         
-   descriptives (mean etc.)
```

```{r sum h index}
summary(df_ego$h_index) 
```

```         
- Overall  (INSERT YEARS STILL)
```

```{r hist h index}

# Histogram of prestige scores for Wave 1 
hist(df_ego$h_index, breaks = 30, main = "Distribution of H-Index from yearX to yearX",     xlab = "H Index", ylab = "Frequency", col = "#B3DE69") # INSERT YEARS OF WAVE/TIME FRAME STILL
```

```         
-   H index per department
```

```{r h index per dep.}
# STILL DO 
```

@@

    ```{r dyad cen}
    # still do 
    ```

@@

    ```{r triad cen}
    # still do 
    ```

@@

    ```{r edge dens}
    #still do 
    ```

@@

    ```{r recip}
    #still do 
    ```

@@

    ```{r degree}
    # still do 
    ```

@@

    ```{r betweenness}
    #still do 
    ```

@@

    ```{r clustering}
    #still do 
    ```

@@

    ```{r density}
    #still do 
    ```

@@

    ```{r path length}
    # still do 
    ```

@@

```{r plot gender}
names(df_ego) #see labels of variables

plot(test_w1,
vertex.color = ifelse(df_ego$gender == 1, "#FB8072", "#80B1D3"), # now, I can use actor attributes for plotting.
# here: if gender = 1 (aka man) then red dot, if not then blue 
vertex.label = NA,
edge.width = 0.2,
edge.arrow.size =0.2)

# if you dont want plot to turn, save the layout (look at SNASS)

>>>>

```{r df_ego data}
df_ego <- fload("./data/processed/df_ego_20241108.rda")

@@

    -   descriptives (mean etc.) in whole sample

```{r sum gender}
summary(df_ego$gender)
```

    - gender counts across whole sample (0 = female, 1 = male)

```{r counts gender-all}
table(df_ego$gender)
```

    -   overall gender distribution in sample

```{r hist gender}
# Histogram of prestige scores for Wave 1  
hist(df_ego$gender, breaks = 2, main = "Distribution of gender",     xlab = "Gender", ylab = "Frequency", col = "#B3DE69") # INSERT YEARS OF WAVE/TIME FRAME STILL
```

    -   Genders per department (0 = female, 1 = male)

```{r gender per dep.}

# Wave 1: Gender count per department 
table(df_ego$discipline.24, df_ego$gender)
```

@@

    -   descriptives (mean etc.)
```{r summary h index}
summary(df_ego$h_index)
```
    - Overall  (INSERT YEARS STILL)

```{r hist h index}
# Histogram of prestige scores for Wave 1 
hist(df_ego$h_index, breaks = 30, main = "Distribution of H-Index from yearX to yearX",     xlab = "H Index", ylab = "Frequency", col = "#B3DE69") # INSERT YEARS OF WAVE/TIME FRAME STILL
```

    -   H index per department

```{r table per dep h index}
# Wave 1: Prestige distribution by dep. and total
df_ego %>%
    group_by(discipline.24) %>%
    summarise(mean_h_index = mean(h_index, na.rm = TRUE), min_h_index = min(h_index,
        na.rm = TRUE), max_h_index = max(h_index, na.rm = TRUE), sd_h_index = sd(h_index,
        na.rm = TRUE)) %>%
    bind_rows(df_ego %>%
        summarise(discipline.24 = "total", mean_h_index = mean(h_index, na.rm = TRUE), min_h_index = min(h_index,
            na.rm = TRUE), max_h_index = max(h_index, na.rm = TRUE), sd_h_index = sd(h_index,
            na.rm = TRUE)))
```

@@

    ```{r dyad cen}

igraph::dyad_census(test_w1)
    ```

@@

    ```{r triad cen}
igraph::triad_census(test_w1)
    ```

@@

    ```{r edge dens}
# edge density
igraph::edge_density(test_w1)
    ```

@@

    ```{r recip}
reciprocity(test_w1, ignore.loops = TRUE, mode = c("default", "ratio"))
    ```
reciprocity = 1 makes sense since the ties are undirected rn

@@

    ```{r degree}

degree_testw1 <- degree(test_w1)
degree_testw1 <- as.data.frame(degree_testw1)
ggplot(degree_testw1, aes(as.numeric(degree_testw1), colour = as.numeric(degree_testw1) )) +
  geom_histogram(binwidth = .9) +
  labs(
    title = "Distribution Degrees Wave 1",
    x = "Distribution of Degrees",
    y = "Count"  ) +
  ylim(0, 65)

@@

    ```{r betweenness}
betweenness_w1 <- igraph::betweenness(test_w1, directed = T)
betweenness_w1 <- as.data.frame(betweenness_w1)
ggplot(betweenness_w1, aes(as.numeric(betweenness_w1), colour = as.numeric(betweenness_w1))) +
  geom_histogram(binwidth = 1.2) +
  labs(
    title = "Distribution Betweenness Wave 1",
    x = "Distribution of Betweenness",
    y = "Count")

@@

    ```{r clustering}
#clustering w1
clustering_w1 <- igraph::transitivity(test_w1, type = "local")
clustering_w1 <- as.data.frame(clustering_w1)
ggplot(clustering_w1, aes(as.numeric(clustering_w1), colour = as.numeric(clustering_w1) )) +
  geom_histogram(binwidth = .05) +
  labs(
    title = "Distribution Clustering Wave 1",
    x = "Distribution of Clustering",
    y = "Count" )
    ```

@@

    ```{r density}
density_w1 <- igraph::edge_density(test_w1)
density_w1
    ```

@@

    ```{r path length}
mean((ego_size(test_w1, order = 2, mode = "out") - 1)/vcount(test_w1))
    ```

@@

### Plotting: Gender 
#### with isolates
```{r plot gender}
# names(df_ego) #see labels of variables

plot(test_w1,
     vertex.color = ifelse(df_ego$gender == 1, "#FFED6F", "#80B1D3"), # now, I can use actor attributes for plotting.
# here: if gender = 1 (aka man) then red dot, if not then blue 
  vertex.label = NA,
  vertex.size = 7.5,
  edge.width = 0.5,
  edge.arrow.size = 0.1,
  main = "Network with isolates [yellow = female, blue = male]")

# if you dont want plot to turn, save the layout (look at SNASS)
```

#### without isolates
```{r removing isolates}
indegr_w1 <- igraph::degree(test_w1, mode = "in")

isolates_w1 <- V(test_w1)[degree(test_w1, mode = "all") == 0]

noisolates_w1 <- delete_vertices(test_w1, isolates_w1)

gsize(noisolates_w1) # edges

gorder(noisolates_w1) # vertices
```

```{r plot wo isolates}
plot(noisolates_w1,
  vertex.color = ifelse(df_ego$gender == 1, "#80B1D3", "#FFED6F"), # now, I can use actor attributes for plotting.
  # here: if gender = 1 (aka man) then red dot, if not then blue 
  vertex.label = NA,
  vertex.size = 9,
  vertex.frame.color = "black",
  edge.curved = 0.2,
  edge.arrow.size = 0.3,
  edge.color = "gray",
  edge.width = 0.2,
  main = "Network without isolates [yellow = female, blue = male]")
```

### Plotting: h-index -ggraph
Credits to Hannah Groennou for the basis of the code of these graphs. 
#### with isolates ?
```{r}

indegr_w1 <- degree(test_w1, mode = "in")

# assign h-index to scholar
V(test_w1)$h_index <- df_ego$h_index
V(test_w1)$indegree <- indegr_w1

#set size of plot
options(repr.plot.width = 15, repr.plot.height = 18)

#plot wave 1 with isolates
p_iso <- ggraph(test_w1,
       layout = "fr") +
  geom_edge_link(color = "#BEBADA", width = 0.5) +
  geom_node_point(aes(size = indegree, color = h_index)) + 
  scale_size(range = c(3, 10)) + 
  scale_color_gradient(low = "red", high = "blue") + 
  theme_void()

p_iso + labs(title = "Network with isolates",
        subtitle = "Plot of indegree and H-index",
        caption = "Data refer to: Scholars RU sociology and political science departments") + theme(plot.title = element_text(hjust = 0.5, face = "bold"), plot.subtitle = element_text(hjust=0.5), plot.caption = element_text(hjust = 1))
```

#### without isolates
```{r}

indegr_w1 <- degree(test_w1, mode = "in")

# assign h-index to scholar
V(test_w1)$h_index <- df_ego$h_index
V(test_w1)$indegree <- indegr_w1

#remove isolates
noisolates_w1 <- delete_vertices(test_w1, V(test_w1)[degree(test_w1) == 0])

#set size of plot
options(repr.plot.width = 15, repr.plot.height = 15)

#plot wave 1 without isolates 
p_noiso <- ggraph(noisolates_w1,
       layout = "fr") +
  geom_edge_link(color = "#BEBADA", width = 0.7) +
  geom_node_point(aes(size = indegree, color = h_index)) + 
  scale_size(range = c(3, 10)) + 
  scale_color_gradient(low = "red", high = "blue") + 
  theme_void()

p_noiso + labs(title = "Network without isolates",
        subtitle = "Plot of indegree and H-index",
        caption = "Data refer to: Scholars RU sociology and political science departments") + theme(plot.title = element_text(hjust = 0.5, face = "bold"), plot.subtitle = element_text(hjust=0.5))

# allowed values for the font face include: “plain”, “italic”, “bold” and “bold.italic”.

##### H-index per department
```{r}
indegr_w1 <- degree(test_w1, mode = "in")

# assign h-index to scholar
V(test_w1)$h_index <- df_ego$h_index
# assign discipline to scholar
V(test_w1)$discipline <- df_ego$discipline.24

V(test_w1)$indegree <- indegr_w1

#remove isolates
noisolates_w1 <- delete_vertices(test_w1, V(test_w1)[degree(test_w1) == 0])

#set size of plot
options(repr.plot.width = 15, repr.plot.height = 15)

#plot wave 1 without isolates 
p_noiso <- ggraph(noisolates_w1,
       layout = "fr") +
  geom_edge_link(color = "#BEBADA", width = 0.7) +
  geom_node_point(aes(size = indegree, color = h_index, shape = as.factor(discipline))) + 
  scale_size(range = c(3, 10)) + 
  scale_color_gradient(low = "red", high = "blue") + 
  theme_void()

p_noiso + labs(title = "Departments without isolates",
        subtitle = "Plot of indegree and H-index",
        caption = "Data refer to scholars from Radboud University.") + theme(plot.title = element_text(hjust = 0.5, face = "bold"), plot.subtitle = element_text(hjust=0.5))

# allowed values for the font face include: “plain”, “italic”, “bold” and “bold.italic”.

### Plotting gender - ggraph 
#### with isolates per department 
```{r}
#assign gender to scholar 
V(test_w1)$gender <- df_ego$gender

# assign discipline to scholar
V(test_w1)$discipline <- df_ego$discipline.24

V(test_w1)$indegree <- indegr_w1

p_gender <- ggraph(test_w1,
  layout = "fr") +
  geom_edge_link(color = "#BEBADA", width = 0.5) +
  geom_node_point(aes(size = indegree, color = as.factor(discipline), shape = as.factor(gender))) +   
  scale_size(range = c(3, 10)) + 
  theme_void()

p_gender + labs(title = "Departments with isolates",
        subtitle = "Plot of indegree and gender",
        caption = "Gender: 0 = female, 1 = male.\n Data refer to scholars from Radboud University.") + theme(plot.title = element_text(hjust = 0.5, face = "bold"), plot.subtitle = element_text(hjust=0.5), plot.caption = element_text(hjust = 1))

#### without isolates per department 
```{r}
#assign gender to scholar 
V(test_w1)$gender <- df_ego$gender

# assign disciplines to scholars
V(test_w1)$discipline <- df_ego$discipline.24
V(test_w1)$indegree <- indegr_w1

#remove isolates
noisolates_w1 <- delete_vertices(test_w1, V(test_w1)[degree(test_w1) == 0])

p_noisgender <- ggraph(noisolates_w1,
  layout = "fr") +
  geom_edge_link(color = "#BEBADA", width = 0.5) +
  geom_node_point(aes(size = indegree, color = as.factor(discipline), shape = as.factor(gender))) +   
  scale_size(range = c(3, 10)) + 
  theme_void()

p_noisgender + labs(title = "Departments with isolates",
        subtitle = "Plot of indegree and gender",
        caption = "Gender: 0 = female, 1 = male.\n Data refer to scholars from Radboud University.") + theme(plot.title = element_text(hjust = 0.5, face = "bold"), plot.subtitle = element_text(hjust=0.5), plot.caption = element_text(hjust = 1))

### Plotting h index and gender -ggraph
#### with isolates 
```{r}
#assign gender to scholar 
V(test_w1)$gender <- df_ego$gender
# V(test_w1)$gender <- ifelse(df_ego$gender >= 0.5,1,0)

# assign h-index to scholar
V(test_w1)$h_index <- df_ego$h_index
V(test_w1)$indegree <- indegr_w1

p_gender <- ggraph(test_w1,
  layout = "fr") +
  geom_edge_link(color = "#BEBADA", width = 0.5) +
  geom_node_point(aes(size = indegree, color = h_index, shape = as.factor(gender))) +   
  scale_size(range = c(3, 10)) + 
  scale_color_gradient(low = "red", high = "blue") + 
  theme_void()

p_gender + labs(title = "Network with isolates",
        subtitle = "Plot of indegree, H-index and gender",
        caption = "Gender: 0 = female, 1 = male.\n Data refer to: Scholars RU sociology and political science departments.") + theme(plot.title = element_text(hjust = 0.5, face = "bold"), plot.subtitle = element_text(hjust=0.5), plot.caption = element_text(hjust = 1))

```
#### without isolates 
```{r gen without iso}
#assign gender to scholar 
V(test_w1)$gender <- df_ego$gender

# assign h-index to scholar
V(test_w1)$h_index <- df_ego$h_index
V(test_w1)$indegree <- indegr_w1

#remove isolates
noisolates_w1 <- delete_vertices(test_w1, V(test_w1)[degree(test_w1) == 0])

p_noisogender <- ggraph(noisolates_w1,
  layout = "fr") +
  geom_edge_link(color = "#BEBADA", width = 0.5) +
  geom_node_point(aes(size = indegree, color = h_index, shape = as.factor(gender))) +   
  scale_size(range = c(3, 10)) + 
  scale_color_gradient(low = "red", high = "blue") + 
  theme_void()

p_noisogender + labs(title = "Network without isolates",
        subtitle = "Plot of indegree, H-index and gender",
        caption = "Gender: 0 = female, 1 = male.\n Data refer to: Scholars RU sociology and political science departments.") + theme(plot.title = element_text(hjust = 0.5, face = "bold"), plot.subtitle = element_text(hjust=0.5))

### 2024-11-12 weekbacktrack.Rmd
prettyplotsindescriptives

| ![](images/socialnetworking.jpg){width="800"}Discussion & conclusion [W]                          | ![](images/used_arson frog.jpg)*[university]*                | ![](images/socialnetworking_meh.jpg){width="800"}*[university]* | ![](images/socialnetworking_meh.jpg){width="800"}[*work, bc I don't want to get fired]*    | ![](images/socialnetworking_meh.jpg)*[university]*                            | *[Catch up on uni]*                                                        | *[Catch up on uni]*                                                      |

>>>>

| ![](images/socialnetworking.jpg){width="800"}Discussion & conclusion [W]                          | ![](images/used_arson%20frog.jpg)*[university]*              | ![](images/socialnetworking_meh.jpg){width="800"}*[university]* | ![](images/socialnetworking_meh.jpg){width="800"}[\*work, bc I don't want to get fired]\*  | ![](images/socialnetworking_meh.jpg)*[university]*                            | *[Catch up on uni]*                                                        | *[Catch up on uni]*                                                      |
